The Neuro Bureau ADHD-200 Preprocessed Repository

### 2015-12-28 Bellec_ADHD200_2016.tex
Updates from ShareLaTeX

Shared preprocessed data and extracted features include:
\begin{itemize}
\tightlist
    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner} \todo{ in figure Sagittal slices are different sizes?})
    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK
    \item Average time series for brain regions from structurally defined parcellations -- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
    \item Average time series for brain regions for regions defined by functional parcellation -- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes})
    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) -- Athena (see Figure~\ref{fig:derivatives})
\end{itemize}

@@

\subsection{NIAK Pipeline}
The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows, implemented in the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}, that perform s-MRI and rs-fMRI processing using a combination of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, and custom Matlab/Octave scripts. The ADHD-200 Sample was processing using NIAK version 0.6.4.1, running on a server of the Canadian Brain Imaging Research Platform (CBRAIN) \cite{sherif2014cbrain}. The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}. The processing scripts for ADHD200 are available on github\footnote{\url{https://github.com/SIMEXP/Projects/tree/master/adhd200}}. 
The log files for execution were included with the derivatives and can be accessed through the PSOM interface\footnote{\url{http://psom.simexp-lab.org/how_to_use_psom.html}}.

@@

Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality calls, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}. Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal (<1mm or degree), moderate (2 to 3 mm or degrees) or severe motion (>3 mm or degrees). The individual results of the NIAK pipeline were visually inspected by M. Chouinard-Decortes for quality of the registration between rs-fMRI and s-MRI data, registration of s-MRI data to template space, and for common artefacts such as ghosting and signal loss. When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory. To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each cite\todo{PB, please verify this}. Additionally the average structural and functional scans after linear and non-linear transformations and the average of all anatomical and functional brain masks for each site of the training and test samples are included as compressed nifti format (.nii.gz)\cite{lavoie2012integration}.

@@

\paragraph{Acknowldegements:} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition. The Athena would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support. The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo. The Burner would like to thank the developers of SPM. The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure\todo{Include other acknowledgements}.

>>>>

Shared preprocessed data and extracted features include:
\begin{itemize}
\tightlist
    \item 3D grey matter density maps suitable for voxel-based morphometry -- Athena and Burner (see Figure~\ref{fig:burner},
    \item 4D preprocessed resting-state fMRI data including limited intermediaries and quality assessment -- Athena and NIAK,
    \item Average time series for brain regions from structurally defined parcellations -- Athena (see Figures~\ref{fig:parcels} and \ref{fig:connectomes}),
    \item Average time series for brain regions for regions defined by functional parcellation -- Athena and NIAK (see Figures~\ref{fig:parcels} and \ref{fig:connectomes}),
    \item Spatial maps for 10 intrinsic connectivity networks (ICNs), fractional amplitude of low frequency fluctuations (fALFF), and regional homogeneity (ReHo) -- Athena (see Figure~\ref{fig:derivatives}).
\end{itemize}

@@

\subsection{NIAK Pipeline}
The NIAK\footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline}} is a collection of workflows, implemented in the Pipeline System for Octave and Matlab (PSOM) \cite{Bellec2012}, that perform s-MRI and rs-fMRI processing using a combination of generic medical image processing modules, the MINC tools\footnote{\url{http://en.wikibooks.org/wiki/MINC}}, and custom Matlab/Octave scripts. The ADHD-200 Sample was processed using NIAK version 0.6.4.1, running on a server of the Canadian Brain Imaging Research Platform (CBRAIN) \cite{sherif2014cbrain}. The NIAK is distributed as an open-source software under MIT license and the code is available on NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=411}} and Github\footnote{\url{https://github.com/SIMEXP/niak}}. The processing scripts for ADHD200 are available on github\footnote{\url{https://github.com/SIMEXP/Projects/tree/master/adhd200}}. 
The log files for execution were included with the derivatives and can be accessed through the PSOM interface\footnote{\url{http://psom.simexp-lab.org/how_to_use_psom.html}}.

@@

Outputs of the NIAK pipeline were subjected to a careful visual inspection and the results quality calls, along with head motion statistics, are available on the NIAK description page \footnote{\url{http://www.nitrc.org/plugins/mwiki/index.php/neurobureau:NIAKPipeline#Quality_control_of_the_preprocessing_-_Training_dataset}}. Estimates of the maximum motion (translation and rotation) between consecutive functional volumes for each rs-fMRI dataset were inspected to categorize the datasets as containing minimal (<1mm or degree), moderate (2 to 3 mm or degrees) or severe motion (>3 mm or degrees). The individual results of the NIAK pipeline were visually inspected by M. Chouinard-Decortes for quality of the registration between rs-fMRI and s-MRI data, registration of s-MRI data to template space, and for common artefacts such as ghosting and signal loss. When substandard registration outcomes were identified, a parameter controlling the non-uniformity correction of the s-MRI was adjusted and the analysis was repeated until the coregistration results were satisfactory. To aid in further quality control, the motion statistics are distributed in comma-seperated values format (.csv) for each site. Additionally the average structural and functional scans after linear and non-linear transformations and the average of all anatomical and functional brain masks for each site of the training and test samples are included as compressed nifti format (.nii.gz)\cite{lavoie2012integration}.

@@

\paragraph{Acknowldegements} The authors would like to thank the ADHD-200 Consortium for assembling and sharing the ADHD-200 Sample and for hosting the ADHD-200 Global competition. The Athena would like to thank the developers of AFNI and FSL, and the Advanced Research Computing at Virginia Tech for computational support. The scripts used to calculate ReHo were generously provided by Dr. Xinian Zuo. The Burner would like to thank the developers of SPM. The NIAK would like to thank the developers of MINC tools, the CIVET pipeline, and the CBRAIN computational infrastructure.
